A Decision Procedure for (Co)datatypes in SMT Solvers

### 2014-12-18 tex/codatadp.tex
more

\begin{verbatim}
primcorec FIXME_x :: "nat tree" where
  "FIXME_x = Node 0 num FIXME_x"

lemma FIXME_x_unique: "x = Node 0 num x \<Longrightarrow> x = FIXME_x"
proof (coinduction arbitrary: x rule: tree.coinduct_strong)
  case (Eq_tree x)
  show ?case
    by (subst (1 2 3 4) Eq_tree) (simp add: eqTrueI[OF Eq_tree])
qed
\end{verbatim}

>>>>

Among the four bisimilarity proofs, three corresponded to one-line
proofs in Isabelle, of the form \keyw{by}~\textit{coinduction}~\textit{auto}
\cite{blanchette-et-al-2014-impl}. The fourth proof was somewhat more elaborate:
%
\begin{quote}
\keyw{lemma} \,\textit{X0\_unique}: \,$x = \const{Node}\;0\;\const{num}\; x \Longrightarrow x = \const{X0}$ \\
\keyw{proof} \,(\textit{coinduction arbitrary}: $x$ \textit{rule}: \textit{tree.coinduct\_strong}) \\
\noindent\hbox{}\quad  \keyw{case} (\textit{Eq\_tree} $x$) \keyw{show} \textit{?case} \\
\noindent\hbox{}\qquad  \keyw{by} (\textit{subst} (1 2 3 4) \textit{Eq\_tree}) (\textit{simp add}: \textit{eqTrueI}[OF \textit{Eq\_tree}]) \\
\keyw{qed}
\end{quote}
%
\noindent
where \const{X0} is defined as $\const{X0} =
\const{Node}\;0\;\const{num}\;\const{X0}$.
